The \dealii{} Library, Version 9.2

### 2020-05-31 9.2/paper.tex
Introdusing transfer of quadrature data of different lengths

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  for a while already
  (e.g., ones in quantum mechanics -- like the equation used in the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems). However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
\item The new \texttt{DiscreteTime} class provides a more
  consistent, more readable, and less error-prone approach to control
  time-stepping algorithms within time-dependent simulations.
  The interface of this class is designed to be minimal
  to enforce a number of important programming invariants, reducing
  the possibility of mistakes in the user code.
  An example is that \texttt{DiscreteTime} ensures that the final time step ends
  precisely on a predefined end time, automatically
  lengthening or shortening to final time step.
\item A key component of \dealii{} are the \texttt{FEValues} and
  \texttt{FEFaceValues} classes that evaluate finite element functions
  at quadrature points located on cells and faces of a cell,
  respectively~\cite{BangerthHartmannKanschat2007}. This release now
  contains a class \texttt{FEInterfaceValues} that considers the
  restriction of the shape functions from \textit{both} sides of a face and
  allows evaluating jumps and averages of shape functions along this
  face. These are common components of the bilinear forms of
  discontinuous Galerkin schemes (as well as schemes for fourth-order
  equations, see the discussion of \texttt{step-47} below) and greatly
  simplify the implementation of these methods.
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.

>>>>

The major changes of this release are:
%
\begin{itemize}
\item xy \todo[inline]{Update once we have the subsections in Section 2;
  provide cross-references to each of these subsections}
%   \item Improved support for automatic differentiation (see
%     Section~\ref{subsec:ad}),
\end{itemize}
%
These major changes are discussed in detail in Section~\ref{sec:major}. There
are a number of other noteworthy changes in the current \dealii{} release
that we briefly outline in the remainder of this section:
%
\begin{itemize}
\item \dealii{} had decent support for solving complex-valued problems
  for a while already
  (e.g., ones in quantum mechanics -- like the equation used in the
  \texttt{step-58} tutorial program covered below -- or for
  time-harmonic problems). However, there were two
  areas in which support was missing. First, the UMFPACK direct solver
  packaged with \dealii{} did not support solving complex-valued
  linear problems. This has now been addressed: UMFPACK actually can
  solve such systems, we just needed to write the appropriate
  interfaces. Second, the \texttt{DataOut} class that is responsible
  for converting nodal data into information that can then be written
  into files for visualization did not know how to deal with vector-
  and tensor-valued fields whose components are complex numbers. An
  example for this is to solve the time-harmonic version of the
  Maxwell equations that has the electric and magnetic fields as
  solution. This, too, has been addressed in this release.
\item The new \texttt{DiscreteTime} class provides a more
  consistent, more readable, and less error-prone approach to control
  time-stepping algorithms within time-dependent simulations.
  The interface of this class is designed to be minimal
  to enforce a number of important programming invariants, reducing
  the possibility of mistakes in the user code.
  An example is that \texttt{DiscreteTime} ensures that the final time step ends
  precisely on a predefined end time, automatically
  lengthening or shortening to final time step.
\item A key component of \dealii{} are the \texttt{FEValues} and
  \texttt{FEFaceValues} classes that evaluate finite element functions
  at quadrature points located on cells and faces of a cell,
  respectively~\cite{BangerthHartmannKanschat2007}. This release now
  contains a class \texttt{FEInterfaceValues} that considers the
  restriction of the shape functions from \textit{both} sides of a face and
  allows evaluating jumps and averages of shape functions along this
  face. These are common components of the bilinear forms of
  discontinuous Galerkin schemes (as well as schemes for fourth-order
  equations, see the discussion of \texttt{step-47} below) and greatly
  simplify the implementation of these methods.
\item Previously, the \texttt{parallel::distributed::ContinuousQuadratureDataTransfer}
  class, which transfers local quadrature point data onto the
  children of newly refined cells, did not allow different regions of the
  triangulation store quadrature data of different lengths. This release lifts
  this restriction, which enables efficient quadrature data storage and data
  transfer within a triangulation containing multiple material models, each with
  their own number of local state variables and history variables.
  As an example, in a solid mechanics simulation, a hyper-elastic material
  model can be assigned to a region of the mesh requiring no history variables
  while another part of the triangulation uses an elasto-plastic constitutive
  model, requiring the storage of local plasticity data at quadrature points.
  During each refinement of the mesh, \texttt{ContinuousQuadratureDataTransfer}
  can be used to transfer and interpolate plasticity data from parent cells to
  their children, ignoring the cells with hyper-elastic constitutive model.
\end{itemize}
%
The changelog lists more than 240 other
features and bugfixes.
